### 2023-03-14 main.tex
typo
ll
jj
Eigsum

\noindent
\textbf{Remark}: The symmetric representations $\lambda=(\twoj,0,\ldots,0)$ are dual to the representations $\lambda=(\twoj,\ldots,\twoj,0)$ that can be obtained via 
\begin{equation}
   \bar E_{ab}=\mu\delta_{ab}-E_{N-b+1,N-a+1}
\end{equation}
{\color{red} This needs to be checked and give alternative form of Hamiltonian?}\\
By the Lie algebra above we describe the process with generator \eqref{Generator}. The state space \eqref{stateSpace} is the vector space with basis elements

@@

\begin{equation}\label{OriginalHamiltonian}
	\begin{split}
		H=\sum_{x,y\in \mathcal{E}}\omega_{x,y}H_{x,y}+\sum_{x\in V}\Gamma_{x}H_{x}
	\end{split}
\end{equation}
where the edge Hamiltonian is
\begin{equation}\label{edgeHamiltonian}
H_{x,y}=\sum_{k,\ell=1}^{N}\left(E_{k\ell}^{x}\otimes E_{\ell k}^{y}-E_{\ell\ell}^{x}\otimes E_{kk}^{y}\right)
 \end{equation}
 and where the site Hamiltonian is
 \begin{equation}\label{siteHamiltonian}
H_{x}=\sum_{k,\ell=1}^{N}\alpha_{k}^{x}\left(E_{k\ell}^{x}-E_{\ell\ell}^{x}\right)
\end{equation}
Here $E_{kl}^{x}$ is a copy of $E_{kl}$ defined in \eqref{actionE} acting on site $x$. 
Following  \cite{belitsky2015self}, the Hamiltonian and the genertor are linked by
\begin{equation}
H=\mathcal{L}^{T}
\end{equation}
The generator can also be expressed as

@@

\begin{align}
	Q_{2L+2}&=A^{2L+1}-\sum_{i=2}^{N}D_{ii}^{2L+1}\\
	Q_{2L+1}&=NA^{2L+1}+A^{2L}-\sum_{i=2}^{N}D_{ii}^{2L}\\
	Q_{2L\phantom{+}}&=NA^{2L}+A^{2L-1}-\sum_{i=2}^{N}D_{ii}^{2L-1}+\sum_{i=2}^{N}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}
\end{align}
The charges $Q_{2L+2}$ and $Q_{2L+1}$ are proportional to the identity matrix, while $Q_{2L}$ contains non diagonal matrices and the boundary parameters $\alpha_{i},\beta_{i}$ $\forall i=2,\ldots,N$.\\
It is easy to show that 
\begin{equation}
	\left[Q_{2L},\widetilde{H}\right]=Q_{2L}\widetilde{H}-\widetilde{H}Q_{2L}=0
\end{equation}
The commutation with the Hamiltonian $\widetilde{H}$ for $Q_{2L+2}$ and $Q_{2L+1}$ is trivial. \\
We introduce the following:
\begin{equation}
Q_{2L}^{0}:=NA^{2L}+A^{2L-1}-\sum_{i=2}^{N}D_{ii}^{2L-1}
\end{equation}
that is 
\begin{equation}
\begin{split}
Q_{2L}^{0}&=N\left(I^{tot}+2e_{11}^{tot}\right)+e_{11}^{tot}(2e_{11}^{tot}+I^{tot})-\sum_{j=2}^{N}e_{jj}^{tot}
\\&
+\sum_{i=2}^{N}\left(	2Ne_{ii}^{tot}+\left(e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}\right)-2\sum_{j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}\right)
\end{split}
\end{equation}
it has the property that commute with the equilibrium Hamiltonian
\begin{equation}
\widetilde{H}_{0}:=\widetilde{B}_{1}^{0}+\mathcal{H}+\widetilde{B}_{L}
\end{equation}
where 
\begin{equation}
\widetilde{B}_{1}^{0}=\begin{pmatrix}
0&0&\ldots&0\\
0&-1&\ldots&0\\
\vdots&\vdots&\ddots&\vdots\\
0&0&\ldots&-1
\end{pmatrix}
\end{equation}
i.e.
\begin{equation}
\left[Q_{2}^{0},\widetilde{H}_{0}\right]=Q_{2}^{0}\widetilde{H}_{0}-\widetilde{H}_{0}Q_{2}^{0}=0
\end{equation}
We also introduce 
\begin{equation}
Q_{2}^{\Delta}:=\sum_{i=2}^{N}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}
\end{equation}
These two matrices $Q_{2}^{0}$ and $Q_{2}^{\Delta}$ are such that
\begin{equation}
Q_{2}=Q_{2}^{0}+Q_{2}^{\Delta}
\end{equation}
We have that the eigenvectors and eigenvalues of the equilibrium case are given by
\begin{equation}
T_{0}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle =\Lambda_{m_{2},\ldots,m_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle
\end{equation}
where $m_{2},\ldots,m_{N}$ denote the total occupation along the chain of species $2,\ldots,N$. Let us notice that $m_{1}=L-\sum_{k=2}^{N}m_{k}$.\\
We make the following ansatz for the eigenvectors of the chain with left triangular and right diagonal boundaries. For the sake of notation, we restrict to the case with $N=3$ and we denote by $\Delta_{2}=\alpha_{2}-\beta_{2}$ and $\Delta_{3}=\alpha_{3}-\beta_{3}$.
\begin{equation}
|\Psi_{m_{2},m_{3}}^{\Delta}\rangle=\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
\end{equation}

@@

>>>>

\noindent
\textbf{Remark}: The symmetric representations $\lambda=(\twoj,0,\ldots,0)$ are dual to the representations $\lambda=(\twoj,\ldots,\twoj,0)$ that can be obtained via 
\begin{equation}
   \bar E_{ab}=\nu\delta_{ab}-E_{N-b+1,N-a+1}
\end{equation}
{\color{red} This needs to be checked and give alternative form of Hamiltonian?}\\
By the Lie algebra above we describe the process with generator \eqref{Generator}. The state space \eqref{stateSpace} is the vector space with basis elements

@@

\begin{equation}\label{OriginalHamiltonian}
	\begin{split}
		H=\sum_{x,y\in \mathcal{E}}\omega_{x,y}H_{x,y}+\sum_{x\in V}\Gamma_{x}H_{x}
	\end{split}
\end{equation}
where the edge Hamiltonian is
\begin{equation}\label{edgeHamiltonian}
H_{x,y}=\sum_{k,\ell=1}^{N}\left(E_{k\ell}^{x}\otimes E_{\ell k}^{y}-E_{\ell\ell}^{x}\otimes E_{kk}^{y}\right)
 \end{equation}
 {\color{red}confusing notation: tensor product and site index.... Remove tensor product?}

 and where the site Hamiltonian is
 \begin{equation}\label{siteHamiltonian}
H_{x}=\sum_{k,\ell=1}^{N}\alpha_{k}^{x}\left(E_{k\ell}^{x}-E_{\ell\ell}^{x}\right)
\end{equation}
Here $E_{kl}^{x}$ is a copy of $E_{kl}$ defined in \eqref{actionE} acting on site $x$. 
Following  \cite{belitsky2015self}, the Hamiltonian and the genertor are linked by
\begin{equation}
H=\mathcal{L}^{T}
\end{equation}
The generator can also be expressed as

@@

\begin{align}
	Q_{2L+2}&=A^{2L+1}-\sum_{i=2}^{N}D_{ii}^{2L+1}\\
	Q_{2L+1}&=NA^{2L+1}+A^{2L}-\sum_{i=2}^{N}D_{ii}^{2L}\\
	Q_{2L\phantom{+}}&=NA^{2L}+A^{2L-1}-\sum_{i=2}^{N}D_{ii}^{2L-1}+\sum_{i=2}^{N}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}
\end{align}
The charges $Q_{2L+2}$ and $Q_{2L+1}$ are proportional to the identity matrix, while $Q_{2L}$ contains non diagonal matrices and the boundary parameters $\alpha_{i},\beta_{i}$ $\forall i=2,\ldots,N$.\\
It is easy to show that 
	\left[Q_{2L},\widetilde{H}\right]=Q_{2L}\widetilde{H}-\widetilde{H}Q_{2L}=0
The commutation with the Hamiltonian $\widetilde{H}$ for $Q_{2L+2}$ and $Q_{2L+1}$ is trivial. \\
We introduce the following:
Q_{2L}^{0}:=NA^{2L}+A^{2L-1}-\sum_{i=2}^{N}D_{ii}^{2L-1}
that is 
Q_{2L}^{0}&=N\left(I^{tot}+2e_{11}^{tot}\right)+e_{11}^{tot}(2e_{11}^{tot}+I^{tot})-\sum_{j=2}^{N}e_{jj}^{tot}
+\sum_{i=2}^{N}\left(	2Ne_{ii}^{tot}+\left(e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}\right)-2\sum_{j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}\right)
it has the property that commute with the equilibrium Hamiltonian
\widetilde{H}_{0}:=\widetilde{B}_{1}^{0}+\mathcal{H}+\widetilde{B}_{L}
\widetilde{B}_{1}^{0}=\begin{pmatrix}
0&-1&\ldots&0\\
0&0&\ldots&-1
i.e.
\left[Q_{2}^{0},\widetilde{H}_{0}\right]=Q_{2}^{0}\widetilde{H}_{0}-\widetilde{H}_{0}Q_{2}^{0}=0
We also introduce 
Q_{2}^{\Delta}:=\sum_{i=2}^{N}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}
These two matrices $Q_{2}^{0}$ and $Q_{2}^{\Delta}$ are such that
Q_{2}=Q_{2}^{0}+Q_{2}^{\Delta}
\subsection{Eigenvector for the diagonal-triangular chain}
In \cite{belliard2011nested}  the eigenvectors and eigenvalues hae been computed for the $gl(N)$ spin chain with diagonal boundaries, therfore we know 
T_{0}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle =\Lambda_{m_{2},\ldots,m_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle
where $m_{2},\ldots,m_{N}$ denote the total occupation along the chain of species $2,\ldots,N$. Let us notice that $m_{1}=L-\sum_{k=2}^{N}m_{k}$.\\
For the sake of notation, we restrict to the case with $N=3$ and we denote by $\Delta_{2}=\alpha_{2}-\beta_{2}$ and $\Delta_{3}=\alpha_{3}-\beta_{3}$ and we further assume that $\Delta_{2}=\Delta_{3}=\Delta$. 
We make the following ansatz for the eigevectors of the diagonal-triangular spin chain:
\begin{equation}\label{ansatzEigenvectorDelta}
|\Psi_{m_{2},m_{3}}^{\Delta}\rangle=\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta^{k_{2}+k_{2}}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}

@@

&\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta^{k_{2}+k_{3}}T_{0}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x) |\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta^{k_{2}+k_{3}+1}\left(B_{2}(x)+B_{3}(x)\right)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta^{k_{2}+k_{3}}\Lambda_{m_{2},m_{3}}(x)G_{m_{2},m_{3}\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
We assume that $G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=G_{m_{2},m_{3},\epsilon}^{k_{2}+k_{3}}(x)$, i.e. it only depends on the sum of $k_{2}$ and $k_{3}$. We make an shift of summation indexes such that 
k_{2}+k_{3}\to k_{2}+k_{3}+1
then we obtain
&\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta^{k_{2}+k_{3}}T_{0}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x) |\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\mathbbm{1}_{\{k_{2}+k_{3}\neq 0\}}\Delta^{k_{2}+k_{3}}\left(B_{2}(x)+B_{3}(x)\right)G_{m_{2},m_{3},\epsilon}^{k_{2}+k_{3}-1}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
\Delta^{m_{2}+m_{3}+1}\left(B_{2}(x)+B_{3}(x)\right)G_{m_{2},m_{3},\epsilon}^{m_{2}+m_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta^{k_{2}+k_{3}}\Lambda_{m_{2},m_{3}}(x)G_{m_{2},m_{3}\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
By equalizing the powers of $\Delta$ we obtain the following condition that must be fulfilled to have that \eqref{ansatzEigenvectorDelta} are indeed the eigenvectors for the triangular-diagonal spin chain:
\item for $k_{2}=k_{3}=0$
\begin{equation}\label{condition1}
T_{0}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}=\Lambda_{m_{2},m_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
\item for $k_{2}+k_{3}\neq 0$
\begin{equation}\label{condition2}
\left[\left(\Lambda_{m_{2},m_{3}}(x)+\epsilon\right)I-T_{0}(x)\right]^{-1}&G_{m_{2},m_{3},\epsilon}^{k_{2}+k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}\\&=\left(B_{2}(x)+B_{3}(x)\right)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
\item finally
\begin{equation}\label{condition3}
\left(B_{2}(x)+B_{3}(x)\right)G_{m_{2},m_{3},\epsilon}^{m_{2},m_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}=0
By chosing 
G_{m_{2},m_{3},\epsilon}^{k_{2}+k_{3}}(x)=\left\{\left[\left(\Lambda_{m_{2},m_{3}}(x)+\epsilon\right)I-T_{0}^{x}\right]^{-1}\left(B_{2}(x)+B_{3}(x)\right)\right\}^{k_{2}+k_{3}}
conditions \eqref{condition1} and \eqref{condition2} are easilly satisfied. To fulfill condition \eqref{condition3}% we can think about $m_{1}:=L-m_{2}-m_{3}$ as the number of empty states in the whole chain. We can further introducte $m:=m_{2}+m_{3}$ and then write $m_{1}=L-m$. Therefore we have an invertivle map between holes and particles, therefore we can think about $\left(B_{2}(x)+B_{3}(x)\right)$ as a lowering operator and 
We make the following ansatz for the eigenvectors of the chain with left triangular and right diagonal boundaries. For the sake of notation, we restrict to the case with $N=3$ and we denote by $\Delta_{2}=\alpha_{2}-\beta_{2}$ and $\Delta_{3}=\alpha_{3}-\beta_{3}$.
|\Psi_{m_{2},m_{3}}^{\Delta}\rangle=\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
